Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-08-21 Documents/M1/realizableFermionicM1/sections/conclusion.tex
Work on the conclusions section

\section{Conclusions}
\label{sec:conclusions}

We develop a realizability-preserving scheme which includes a suitable CFL condition, a realizability-preserving limiter, a realizability-preserving closure procedure and a realizability-preserving IMEX time integrator.
Thanks for the meaningful result domain being a convex set, the realizability-preservation of the limiter and the IMEX time integrator can be ensured by requiring they have convex combination forms.
And a realizability-preserving closure procedure can be obtained by any closure procedure building on Fermi-Dirac statistics.
In the physics which we interested, the transport system introduces a stiff problem: the collision term has much larger eigenvalues than that the advection term has.
Therefore, requiring the scheme be streaming accurate and diffusion accurate is an essential and achievable goal than being overall accurate.
We purpose our PD-ARS scheme. It is 2nd-order accurate and strong stability preserving in the streaming limit and works well in the diffusion limit. Numerical examples are provided to demonstrate those properties.

It's widely known that a realizability-preserving scheme is required for solving the approximating transport problems with conservation law, including the two-moment model.
However, few people are aware of the significance of realizability-preserving closure procedure: the Minerbo closure, which is not built on Fermi-Dirac distribution, is widely used.
We highly recommend the CB closure other than the Minerbo closure because the CB closure not only preserves the realizability but also requires no more calculation than the Minerbo closure.

The realizability-preservation of our IMEX scheme is universal: it can be implemented to any problems where the physical constraints confine its meaningful result to a convex set and the diffusion limit is important.

To build this work, we assume an easy collision term and no relativistic term on the left-hand side of the transport equation.
Hence, to solve a more realistic problem, a complex collision term and some relativistic terms should be taken into consideration.
Besides, a higher order accurate method is always desired.
Moreover, there is no reason to restrict the time integrator to be IMEX.
They all bring the remained open problems which require the future contribution.

>>>>

\section{Summary and Conclusions}
\label{sec:conclusions}

We have developed a realizability-preserving DG-IMEX scheme for a two-moment model for fermion transport.  
The scheme employs simple algebraic two-moment closures rooted in Fermi-Dirac statistics, and combines a CFL condition, a realizability-enforcing limiter, and a constraint-preserving time integrator to maintain point-wise realizability of the moments.  
Since the realizable domain is a convex set, the realizability-preserving property is obtained from convexity arguments, building on the framework in \cite{zhangShu_2010a}.

In the applications motivating this work, the collision term is stiff in regions of the computational domain, and we have considered IMEX schemes to avoid solving the transport operator implicitly.  
We considered recently proposed second-order accurate, constraint-preserving IMEX schemes (cf. \cite{chertock_etal_2015,hu_etal_2018}), which restore second-order accuracy with an implicit correction step.  
However, we are unable to prove realizability (without invoking a very small time step) with the approach in \cite{chertock_etal_2015}, and we have demonstrated that the approach in \cite{hu_etal_2018} does not perform well in the diffusion limit.  
For these reasons, and the general nonexistence of high-order, implicit SSP-RK schemes \cite{gottlieb_etal_2001}, we have resorted to develop first-order, constraint-preserving IMEX schemes.  
While the proposed scheme (dubbed PD-ARS) is formally only first-order accurate, it works well in the diffusion limit, is constraint-preserving with a reasonable time step, and reduces to the optimal second-order accurate SSP-RK scheme in the streaming limit.

For each stage of the IMEX scheme, the cell-averaged moments can be written as a convex combination of forward Euler steps (implying the Shu-Osher form for the explicit part), followed by a backward Euler step.  
Realizability of the explicit part requires the DG solution to be realizable in a finite number of quadrature points in each element and the time step to satisfy a CFL condition.  
For the backward Euler step, realizability of the cell-averages follows easily from the simple form of the collision operator (which includes emission, absorption, and isotropic elastic scattering), and is independent of the time step.  
The CFL condition is then solely due to the transport operator, and the time step can be as large as that of the forward Euler scheme applied to the explicit part.  
After each update, the limiter enforces realizability point-wise by damping towards the realizable cell average.  
Numerical experiments are presented to demonstrate the accuracy and realizability-preserving property of the scheme.  
The applicability of the PD-ARS scheme is not restricted to the fermionic two-moment model.  
It may therefore be a useful option in other applications of kinetic theory where physical constraints confine solutions to a convex set and capturing the diffusion limit is important.

Realizability of the fermionic two-moment model depends sensitively on the closure procedure.  
For the simple algebraic closures adapted in this work, realizability of the scheme demands that lower and upper bounds on the Eddington factor are satisfied \cite{levermore_1984,lareckiBanach_2011}.  
The Eddington factors deriving from the maximum entropy closures of Cernohorsky \& Bludman \cite{cernohorskyBludman_1994} and Larecki \& Banach \cite{lareckiBanach_2011}, and the Kershaw-type closure of Larecki \& Banach \cite{banachLarecki_2017a} satisfy these bounds, and are suitable for the fermionic two-moment model.  
Further approximations of the closure procedure, e.g., employing the low occupancy limit, which results in the Minerbo closure \cite{minerbo_1978} when starting with the maximum entropy closure of \cite{cernohorskyBludman_1994}), is not compatible with realizability of the fermionic two-moment model, and we caution against this approach to modeling particle systems governed by Fermi-Dirac statistics; particularly if the low occupancy approximation is unlikely to hold (e.g., when modeling neutrino transport in core-collapse supernovae).

In this work, we considered a relatively simple model.  
In particular, we adopted Cartesian coordinates, assumed a linear collision operator and a fixed material background, isotropic elastic scattering, and relativistic effects due to interactions with a moving background or the presence of a strong gravitational field were not included.  
To solve more realistic problems of higher scientific interest, some or all of these physical effects must be included.  
In the context of constraint-preserving schemes, these extension provide significant challenges suitable for future investigations, and for which the scheme presented here may serve as a foundation.
